MASU Paper

### 2022-05-31 paper/paper_draft.Rmd
Updated discussion

# Discussion 
## Results Discussion
According to the PCA, there is overlap between the anadromous and resident individuals from both populations. Although having overlapping clusters does not exclude the possibility of a genetic influence, our findings did not clearly show associated genetic elements between resident and anadromous fish. As mentioned in the previously to look for patterns in relatedness between resident and andromous individuals, we calculated the mean PC1 and PC2 coordinates for each stream, then calculated the distance between each individual sample and the mean for the other population. It is important to note that we did find that anadromous individuals were more closely related to individuals in the other population. 
<!-- This can potentially be attributed to where the samples were collected. For example, if the anadromous individuals from one stream were collected in an area that was geographically near the individuals in the other stream, this could explain this observation. (not sure how to interpret the metadata to confirm this) -->
We also made a manhattan plot and did not find many individuals that had a locus with a high p-value. This indicates that there is not an area in the genome that is strongly associated with the given trait (anadromy vs. resident). The random forest also did not have strong predictive power for anadromy and residency because it could not accurately group the individuals to their actual life cycle. 
Overall there is not strong evidence for a genetic influence that determines the MASU salmon's life cycle.

## Ramifications for MASU salmon
In these populations it is possible that residency and anadromy within MASU salmon are not solely genetica lly controlled and that we must take into consideration the environmental influences. When comparing MASU salmon to steelhead, steelhead and their life cycles are more heavily influenced by genetic factors. As of now, MASU salmon and their life cycles are mainly influenced my environmental factors, but further studies with larger sample sizes would need to be conducted in order to see if any genetic influences play a role. In other words, we would need still need to figure out if MASU salmon life cycles are influenced by the additive effects of genetics and environment, the multiplying effetcs of genetics and environment, or simply a result of purely environmental effects.

<!-- talk about genetic mechanism in steelhead and how that varies in environmental  -->
## Ramifications for Salmonids in General 
In terms of the importance of this work, figuring out if MASU salmon life cycles have genetics influences will go towards their conservation efforts. For example, within steelhead fish, anadromous individuals will have to migrate upstream in order to move towards the ocean. On some occurrences the anadromous steelhead will be stopped midway towards their journey to the ocean due to manmade dams. This has caused a reduction in diversity within these fish by causing an apparent increase in resident individuals within the population. Knowing whether a fish is anadromous or resident would be helpful because people can advocate for dams to built in areas where there are a lot of anadromous fish. This same logic can also be applied towards the conservation of MASU salmon.

>>>>

# Discussion
## Genetic Associations with Migration

We did not find any significant genetic associations with migratory phenotype (see Figure X). This indicates that in the streams we examined, there may not be any loci in the genome that strongly contribute to migratory life history decisions. It is not therefore surprising that the random forest which we conducted also did not have strong predictive power for anadromy and residency, since it would not be able to accurately group the individuals to their actual life history if there are no genetic elements that contribute to migratory phenotype.

However, our study included samples from only a small region at the center of the masu range. It is possible that if we sampled from other areas, we could uncover loci that influence migratory life history phenotypes under environmental conditions that differ from those in our study systems. This could occur if the effect of migratory genes depends on environmental conditions (GxE). This phenomena is seen in steelhead, where variance in environmental conditions across the species’ range can determine whether life histories are more genetically or environmentally based (CITE).

## Patterns of Relatedness Between Anadromous and Resident Individuals

We found that although our two populations (TK and CH) were genetically distinct from one another, there was substantial overlap between the anadromous and resident individuals within each population, indicating that resident and anadromous individuals freely interbreed within populations. Interestingly, we did find that anadromous individuals were significantly more closely related to individuals from the stream from which they did not originate. This could potentially be attributed to where the samples were collected. For example, if the anadromous individuals from one stream were collected closer to the river mouth than residents, and thus geographically closer to the other stream, this could explain why we observed that they were more genetically similar to individuals from that stream. Alternatively, if anadromous individuals are more likely to stray than residents (since they may return to the wrong river system), and their offspring are more likely to be anadromous themselves, then this could also produce the pattern we observed.

However, this hypothesis could only be true if there are transgenerational environmental or genetic correlations with anadromy. Given that we did not find any obvious genetic associations with anadromy, the latter seems more likely. For example, transgenerational environmental correlations anadromy could exist if anadromous individuals tend to breed in areas where there are less nutrients available, since smaller body sizes induce the decision of an anadromous life cycle. Under these circumstances, the offspring of migrants would be more likely to be migrants themselves, allowing for the localized build up of alleles brought in by strays.

## Conservation Ramifications
Our results suggest that, at least in some areas, residency and anadromy within masu salmon are not significantly genetically controlled and that fisheries managers and conservation groups should therefore focus more on the possible environmental correlations with migration (such as temperature and resource availability) when planning conservation efforts targeting masu salmon. Unfortunately, this also means that genetic monitoring for the anadromous potential of a stream is probably often not possible, since it is not possible to predict migratory phenotype from genotypic data. These results may not extrapolate across the entire masu range: further studies with larger sample sizes from more areas could help determine if migratory life history decisions are influenced by the additive or multiplicative effects of genetics and environment or simply a result of purely environmental effects across the full range of the species.
